Coronal Fourier power spectra: implications for coronal seismology and coronal heating

### 2014-10-07 tex/paper1/paper1.tex
final revision complete

\subsection{Results}\label{ssec:results}
Figure \ref{fig:fit171193} show the fit results of each model to the
data.  For details on the fitting procedure, see Appendix
\ref{sec:app:ind}.

{\BF The two models are assessed for how well they describe the data in two
different ways. Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that Model 2 loses less information compared to Model 1,
leading to a preference for Model 2 over Model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
{\BF The AIC reveals which (out of a set of models) is preferred.  It
  does not give an assessment of the goodness-of-fit of each model.
  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
  $\chi^{2}_{r}=\sum_{j=1}^{N}\left[(P_{i}(\nu_{j})-D_{j})/\sigma_{j}^{2}\right]/(N-k-1)$,
  where $N=899$ is the number of frequencies, $P_{i}(\nu_{j})$ is the
  model power $P_{i}$ at frequency $\nu_{j}$, $D_{j}$ is the \mFpa\ at
  $\nu_{j}$, and $\sigma_{j}$ is the estimated standard deviation of
  the data $D_{j}$ (see Appendix \ref{sec:app:ind} for more details of
  the estimation of $\sigma_{j}$).  The value of $\chi^{2}_{r}$ is
  calculated for both models.  Note that the \mFpa\ are only
  approximately normally distributed, and so caution must be used in
  interpreting $\chi^{2}_{r}$. Since $N>>k$, $\chi^{2}_{r}$ is
  understood as a measure of the average scaled variance of the model
  fit to the data. Within the approximations of the analysis, the
  $\chi^{2}_{r}$ measures show that reasonable fits are obtained for
  Model $M_{2}$ in all cases, excepting the loop footpoints.  The
  relatively low value of $\chi^{2}_{r}$ for these locations indicate
  that probably the size of $\sigma_{i}$ are over-estimated.}

@@

Each emission event is modeled as an exponentially decaying function
of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{total}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
emission $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the total emission in each event depends on its time scale $T$
such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed \PS\ can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P_{total}(\nu) \propto \nu^{-(2-\alpha_{E})(1+\gamma)}.
\end{equation}
This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar emission events.

This derivation of a \PL\ \PS\ shares many similar features with the
nanoflare model of {\it energy} deposition in the solar atmosphere. In
the nanoflare model advanced by \cite{1988ApJ...330..474P}, large
numbers of small magnetic reconnection events convert the energy in
the magnetic field into energy that heats the corona.  Nanoflares are
hypothesized to be small ($10^{24}-10^{27}$ ergs) yet ubiquitous in
the corona.  \cite{2013ApJ...771...21W} and \cite{2013ApJ...770L...1T}
analyzing narrowband 193\AA\ images taken by the Hi-C instrument on
board a sounding rocket demonstrate the heating of small scale coronal
structures that appear to be consistent with scenarios of nanoflare
heating due to reconnecting magnetic loops.  However, the nanoflare
occurence rate, or their energy distribution for the entire solar
atmosphere is as yet unknown.

>>>>

\subsection{Results}\label{ssec:results}
Figure \ref{fig:fit171193} show the fit results of each model to the
data.  For details on the fitting procedure, see Appendix
\ref{sec:app:ind}.
{\BF The two models are assessed for how well they describe the data in two
different ways. Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that Model 2 loses less information compared to Model 1,
leading to a preference for Model 2 over Model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
{\BF The AIC reveals which (out of a set of models) is preferred.  It
  does not give an assessment of the goodness-of-fit of each model.
  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
  $\chi^{2}_{r}=\sum_{j=1}^{N}\left[(P_{i}(\nu_{j})-D_{j})/\sigma_{j}^{2}\right]/(N-k-1)$,
  where $N=899$ is the number of frequencies, $P_{i}(\nu_{j})$ is the
  model power $P_{i}$ at frequency $\nu_{j}$, $D_{j}$ is the \mFpa\ at
  $\nu_{j}$, and $\sigma_{j}$ is the estimated standard deviation of
  the data $D_{j}$ (see Appendix \ref{sec:app:ind} for more details of
  the estimation of $\sigma_{j}$).  The value of $\chi^{2}_{r}$ is
  calculated for both models.  Note that the \mFpa\ are only
  approximately normally distributed, and so caution must be used in
  interpreting $\chi^{2}_{r}$. Since $N>>k$, $\chi^{2}_{r}$ is
  understood as a measure of the average scaled variance of the model
  fit to the data. Within the approximations of the analysis, the
  $\chi^{2}_{r}$ measures show that reasonable fits are obtained for
  Model $M_{2}$ in all cases, excepting the loop footpoints.  The
  relatively low value of $\chi^{2}_{r}$ for these locations indicate
  that probably the size of $\sigma_{i}$ are over-estimated.}

@@

Each emission event is modeled as an exponentially decaying function
of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{total}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
emission $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the total emission in each event depends on its time scale $T$
such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed \PS\ can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P_{total}(\nu) \propto \nu^{-(2-\alpha_{E})(1+\gamma)}.
\end{equation}
This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar emission events.  {\bf Equation
  \ref{eqn:finalfps} extends a suggestion by
  \citet{1991SoPh..133..357H} that Equation \ref{eqn:ftexpdecay} be
  used to estimate the timescale of a number of smaller heating events
  with identical timescale $T$ in a sufficiently long span of solar
  X-ray observations. \citet{1991SoPh..133..357H} is extended by
  considering a distribution of heating event timescales (Equation
  \ref{eqn:energydistrib}) as opposed to a single timescale.}

The derivation of the \PL\ \PS\ Equation \ref{eqn:finalfps} shares
many similar features with the nanoflare model of {\it energy}
deposition in the solar atmosphere. In the nanoflare model advanced by
\cite{1988ApJ...330..474P}, large numbers of small magnetic
reconnection events convert the energy in the magnetic field into
energy that heats the corona.  Nanoflares are hypothesized to be small
($10^{24}-10^{27}$ ergs) yet ubiquitous in the corona.
\cite{2013ApJ...771...21W} and \cite{2013ApJ...770L...1T} analyzing
narrowband 193\AA\ images taken by the Hi-C instrument on board a
sounding rocket demonstrate the heating of small scale coronal
structures that appear to be consistent with scenarios of nanoflare
heating due to reconnecting magnetic loops.  However, the nanoflare
occurence rate, or their energy distribution for the entire solar
atmosphere is as yet unknown.
